Who Get More Money, Attention and Handshakes? Chinese Foreign Aid and Debt, Xinhua and Diplomatic Visits

### 2022-11-15 04_paper/1114_draft_LL.Rmd
Ready to go!!!

---
title: "Friends Get More Money, Attention and Handshakes: Chinese Foreign Aid and Debt, Xinhua and Diplomatic Visits"
author: ["Lucie Lu","Miles D. Williams"]
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  bookdown::pdf_document2: 
    toc: false
classoption: fleqn
fontfamily: mathpazo
fontsize: 12pt
bibliography: ref_xinhua.bib
link-citations: yes
linkcolor: blue
header-includes:
  - \usepackage{amsmath}
  - \usepackage{setspace}
  - \setlength{\mathindent}{15pt}
  - \setlength\parindent{24pt}
  - \setlength{\parskip}{0.0pt plus 1.0pt}
  - \doublespacing
  - \newtheorem{theorem}{Theorem}[section]
  - \newtheorem{lemma}[theorem]{Lemma}
  - \newtheorem{proposition}[theorem]{Proposition}
  - \newtheorem{corollary}[theorem]{Corollary}
  - \newenvironment{proof}[1][Proof]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries Proof}]}{\end{trivlist}}
  - \newenvironment{definition}[1][Definition]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries 1}]}{\end{trivlist}}
  - \newenvironment{example}[1][Example]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries 1}]}{\end{trivlist}}
  - \newenvironment{remark}[1][Remark]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries 1}]}{\end{trivlist}}
  - \newcommand{\qed}{\nobreak \ifvmode \relax \else
      \ifdim\lastskip<1.5em \hskip-\lastskip
      \hskip1.5em plus0em minus0.5em \fi \nobreak
      \vrule height0.75em width0.5em depth0.25em\fi}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \floatplacement{figure}{!t}
  - \usepackage{caption}\captionsetup[table]{skip=5pt}
  - \usepackage{dcolumn}
  - \usepackage{rotating}
  - \usepackage{caption}\DeclareCaptionLabelFormat{AppendixTables}{A.#2}

abstract: "Absent formal avenues of transparency, how do China’s foreign aid and debt allocation relate to public diplomacy and international recognition efforts? We bring a novel perspective to this issue by considering Chinese media coverage of developing countries intended for foreign audiences and China’s bilateral diplomatic activities. We propose that despite the lack of formal reporting, Beijing can pursue international recognition and diplomacy with its overseas financing with the help of other complementary foreign policy activities. We expect greater coverage of a developing country in a Chinese outward-facing media outlet and bilateral diplomatic activity to correlate with greater aid giving and debt allocation. To test this expectation, we leverage (1) AidData’s Chinese development finance datasets and (2) the meta-data of millions of Xinhua news articles in the Cline Center for Advanced Social Research. We find that China pays more media attention to aid recipients but engages more in diplomatic visits with debtors. Aid-recipient countries disproportionately get more media coverage on the state of their economy and developmental needs. Also, China is more likely to provide loans to diplomatically aligned countries. Our results dispel the myths of China as a ’rouge donor’ of desigining ’debt-trap diplomacy.’ We suggest that much like traditional donors, China’s foreign aid and debt allocations present a versatile foreign policy tool in international politics. "
---

@@

Although Beijing has primarily focused on its immediate surrounding neighbors, Asia-Pacific and Central Asia, for security and geostrategic concerns, it is nevertheless increasingly thinking and acting globally [@nathan_chinas_2012]. Similarly, in terms of where China's money goes and its economic influence is concentrated, some countries clearly are more important than others. However, Beijing's leaders hold the reasons why close to the vest.

The secrecy surrounding China's international development financing is puzzling. But vis-$\grave{\text{a}}$-vis the limited transparency, the painstaking work of researchers to document and analyze trends in China's development financing has illuminated a great deal about Beijing's approach to giving and lending. In one of the most comprehensive and thorough efforts to document trends in Chinese development finance, @dreher_banking_2022 find that China is far from the rogue donor that many have feared, but instead, China's ODA-like expenditures follow patterns similar to those of OECD-DAC donors. Hence, much like these traditional donors, China's foreign aid presents as a versatile foreign policy tool through which Beijing seeks to accomplish important objectives in international politics. These goals include international recognition that China is a great power and closer diplomatic ties with developing countries in what China calls "South-South" cooperation.

However, the goals of facilitating cooperation and winning international recognition as a rising power are difficult to accomplish in secret. This, therefore, raises a natural question. *How do China's foreign aid and debt allocation relate to its public diplomacy and international recognition efforts?*

We propose that despite the lack of formal reporting, Beijing can pursue international recognition and diplomacy with its overseas financing with the help of other complementary foreign policy activities. Specifically, we consider outward-facing state-sponsored news coverage and bilateral diplomatic missions from Beijing. Past research suggests that these two activities play special roles in complementing the foreign policy objectives that drive China's giving and lending.

While public diplomacy and outward-facing state-sponsored media are not solely used to support China's overseas development financing, we believe they have clear overlapping purposes. In particular, diplomacy and coverage are critical *visible* activities that can complement the often opaque character of Beijing's development finance. Thus, to the extent that China's development finance is targeted at supporting image- and alliance-building activities, we hypothesize that recipients of China's overseas development assistance will also be disproportionate targets of media coverage in *Xinhua* to support China's image abroad and to build publicity around its development activities, and they will be more frequent hosts of diplomatic missions from Beijing to support closer bilateral cooperation.

As we test these hypotheses, in our research design we delineate China's development financing according to the type of assistance China offers. Until recently, many have mistakenly conflated Beijing's ODA-like giving with its other official financing (OOF). However, efforts to disentangle China's activities with respect to grants and low-interest loans (financing that would meet the OECD definition of official development assistance or ODA) from its activities with respect to higher interest loans and export credits (OOF) have unmasked a considerable divergence in goals. The conventional view is that while *aid* (ODA) is closely tied to Beijing's foreign policy goals, *debt* (OOF) is related to Beijing's commercial interests.[^1] Thus, as we test our hypotheses, we also distinguish between Beijing-as-donor from Beijing-as-lender.

@@

We find that there are a few overlaps between the top 20 countries that receive aid and loans from Beijing at the same time. In other words, China target its aid and debt to different sets of developing countries. However, the neat distinction between China's use of aid and debt does not imply these tools serve separate goals, policy or commercial oriented ones, as conventional view holds. In particular, we find that *Xinhua* coverage is disproportionately concentrated among China's aid recipients, while no significant relationship exists between aid and diplomatic visits. Conversely, we find that debt is significantly linked to a greater frequency of bilateral diplomatic missions from Beijing, but no significant difference in *Xinhua* coverage. Together these findings reveal an intriguing pattern: Beijing likes to talk about its aid recipients but prioritizes diplomatic visits with its debtors.

On the one hand, aid recipient countries disproportionately get more media coverage from *Xinhua* via stories that report both on the state of their economy and their development needs. Notably, *Xinhua* does not just promote China's efforts to offer aid to those countries in need but also gives a rounded picture of those countries' economic conditions justifying their legitimate need for aid. On the other hand, China engages in more conventional forms of bilateral diplomacy via government-to-government diplomatic missions to cement closer bilateral ties with debtors.

These findings contradict with what conventional views hold that Beijing has tried to keep its giving secret. Instead, *Xinhua* devotes significant media attention and resources to Beijing's aid-recipients. It may help to promote Chinese roles and efforts in the developmental trajectories of these countries and improve Chinese image through visual branding of aid. Furthermore, China is not shy away from its ambition in building closer bilateral cooperation with its debt-recipients to align with their foreign policy goals. In addition to lending money, China engages in building and strengthening the friendships with these countries. Economic interests to motivate Beijing's debt allocations are suggestive to be secondary to its policy goals.

Meanwhile, the finding that loans corresponding with diplomatic missions has special relevance in light of Beijing's Belt and Road Initiative (BRI). A 2018 BRI foreign policy assessment report from Washington [@hurley_examining_2019] highlights that lending indicates Beijing's economic interests and strategic dominance---China tends to lend to vulnerable states with debt distress in exchange for unfair deals and strategic concessions. Brautigam [-@brautigam_critical_2020] calls the Chinese "debt-trap diplomacy" as a meme based on collective fear of the Chinese threat rather than sound empirical evidence. Our finding suggests that China is more likely to provide loans to diplomatically aligned countries. For instance, Russia, one of China's closest allies, receives the highest amount of lending on average among 142 countries but no aid at all between 2002 and 2017. In contrast, Iraq shows the opposite pattern: it receives the highest amount of aid from China during the period of our investigation, but it does not receive any loans. Concern about Chinese debt nonetheless raises a natural question related to the function of diplomacy in debtor countries. Does debt serve as a tool of diplomacy, or does Beijing wield diplomacy to cover a multitude of "debt-trap" sins? This study sheds some light on this pressing question, but further research is needed to fully answer it.

@@

China's motivations for giving foreign aid to developing countries mirror, in many ways, the motivations of Western donors. While recipient needs, in part, predicate Chinese assistance, so do Beijing's political and economic interests. Evidence suggests that China targets more finance toward poorer countries and does not systematically favor authoritarian over democratic recipients [@dreherEtAl2018]. At the same time, China gives more aid to countries that import more goods from China, while it gives less aid to those that officially recognize Taiwan [@dreherFuchs2015]. Further, China's Official Financing disproportionately goes to countries with more natural resources, greater UN General Assembly voting alignment with Beijing, and with more capacity to repay loans [@dreherEtAl2021].

Two waves of surveys of policymakers in 126 countries demonstrate the diplomatic impact that these investments have had.[^2] Compared to a first survey wave in 2014, responses in 2017 showed an increase in evaluations of China's influence with policymakers in developing countries. It would be naive to suppose this is a side-effect, rather than a goal, of China's development finance and other investments.

@@

If its diplomatic motives for giving aid parallel those of other donor governments, visibility is surely a major concern for Beijing. Visual branding of aid has emerged as a growing concern among donors. The United States Agency for International Development (USAID), for example, cited its "new 'brand identity'" as instrumental in promoting the visibility of 2004-2005 tsunami relief to Indonesia.[^3] A US State Department report from 2004 further claims that better branding contributed to a doubling of favorable attitudes toward the US. Pew Research supports this view, finding that nearly 80$\%$ of Indonesians surveyed "said that post-tsunami aid from the US had improved their impression of America."[^4]

@@

On the one hand, since aid is supposed to have more direct links to China's foreign policy goals, it follows that China will complement its aid giving with visible acts of diplomacy and efforts to increase the salience of aid recipients in foreign audiences. On the other hand, while aid and debt may have distinct goals, such a tidy distinction may be too simplistic. Perhaps more importantly, some of the market oriented objectives that drive China's global debt might benefit from public displays of diplomacy. On this front, recent research suggests that Beijing uses its debt to ensure access to natural resources that China lacks domestically. As noted above, @dreherEtAl2021 find that Beijing targets more of its loans in resource rich developing countries, a strategy that @dreher_banking_2022 contend is meant to guarantee access to said resources. When Beijing's policy banks provide these loans, developing country governments collateralize their oil or rare minerals, all but assuring access to these resources for Beijing since many of these countries are unable to directly repay the loans [@dreher_banking_2022].

@@

This paper will focus on Xinhua outward-facing English branch whose audiences are primarily English-speaking readers. Simply providing more information will not improve their image in the Western world. Attracting audiences depends on credibility, a state-sponsored-image-construction news outlet would typically lack. As Druckman (2001) presents, one conditional factor in influencing public opinion (especially foreign audiences'), is an information sender's "credibility." On the one hand, governments attempt to positively shape the global narrative regarding their leaders and foreign policies using their own newsgathering and broadcasting operations. On the other hand, Xinhua needs to maintain a low political bias and higher professional standard to assert its brand and increase its international competitiveness.

@@

Government-to-government visits are important as leaders' resources are scarce. They often mark the further development in bilateral relations, especially in furthering the visiting and host countries' bilateral trade relationships [@nitsch_state_2005]. Leader visits also have implications on the host leaders' security in office [@malis_state_2021] and the states' security issues [@mcmanus_making_2018]. In all, diplomatic visits send important an important positive signal that the visiting and hosting countries support each other and have closer relationships.

Visiting leaders can increase the awareness of themselves and their country among citizens in the host country. Goldsmith and Horiuchi [-@goldsmith_spinning_2009] find that the impact of high-level government visits on foreign publics' opinions is contextual. U.S. visits had large and positive impact until the international media reported the negative aspects of the "war on terror" in Iraq. Again, credibility of a country's leadership is the key to conditioning the effects of high-level visits on the foreign public's perception of the country's policy. The most recent finding shows that high-level diplomatic visits across the board can improve the public approval of the visiting leader's job performance by a significantly large effect. The positive messages are especially contingent on how the public-diplomacy activities are mentioned in the news in the host countries [@goldsmith_does_2021]. In most cases, the host leader has leverage to provide frame for the journalists to report the government-to-government visit that is expected to receive positive coverage.

@@

Since both approaches feature scarce time and resources, we expect that Beijing will choose on whom to cast the spotlight and to visit strategically. Most importantly for China's overseas development financing, coverage and diplomatic visits are immediate visible signals of Beijing's priorities. For this reason, Beijing may use both as a way to complement related political objectives it seeks to promote via its financing activities.

To test this logic, we examine the extent to which recipients of Chinese overseas development financing also receive disproportionate coverage in *Xinhua* and host a disproportionate number of diplomatic missions from Beijing. We further leverage data both on Chinese ODA (aid) and Chinese OOF (debt) in testing these relationships. As noted earlier, while aid is thought to correspond with Beijing's foreign policy goals, debt is supposedly linked to its comercial goals. We therefore should expect *Xinhua* coverage and diplomatic visits to be closely linked with Chinese aid, while these outcomes should be independent of Chinese debt.

@@

If we can reject the null hypothesis for H1 and H2 this will be consistent with the view that China uses aid for political goals. Conversely, H3 and H4 are themselves null hypotheses. If these can be rejected, this will count as evidence that, in fact, debt is not independent of foreign policy objectives as the literature claims [@dreher_banking_2022]. The next section describes our data and research design for testing these hypotheses.

@@

To test hypotheses 1-4 we rely on zero-inflated negative binomial regression models using yearly counts at the recipient-year level of the number of *Xinhua* article mentions and the number of bilateral diplomatic visits from Beijing as the response variables, respectively. Since these outcomes reflect discrete counts, we apply a method that explicitly models a discrete count process. We opt for negative binomial regression rather than Poisson since the variance of the outcomes is not equivalent to their means. We further apply the zero-inflated negative binomial model since the distributions of yearly coverage counts and visits contain a substantial number of zero values. Because of the panel nature of the data, we further include random recipient intercepts in model estimation to account for within-recipient dependence and additional unobserved recipient heterogeneity.

@@

Models 1 and 2 each include year intercepts to adjust for yearly shocks and changes to Beijing's overall aid and debt portfolio, denoted by the term $\tau_t$. The parameter $\rho_i$ denotes random recipient intercepts. The vector $X_{it}$ denotes a set of control variables to improve precision and to adjust for possible confounders for Chinese bilateral financing, *Xinhua* coverage, and diplomatic visits. A summary of these variables, any transformations applied, and their sources is given in Table [x].

[Table x goes here]

@@

## Main variables

*aid, debt, Xinhua mentions, diplomatic visits*

@@

Alongside these shifts in the application of aid and debt in Beijing's approach to international development finance, a consensus has evolved that aid and debt serve different functions for China. Aid is supposed to support China's foreign policy goals, while debt is supposed to support its market interests [see @dreher_banking_2022]. The idea is that aid lets Beijing buy influence, whereas debt helps enrich Chinese firms and propel economic growth for China. However, an examination of patterns in the main variables of interest in this study problematizes this tidy distinction.

>>>>

---
title: "Who Get More Money, Attention and Handshakes? Chinese Foreign Aid and Debt, Xinhua and Diplomatic Visits"
author: ["Lucie Lu","Miles D. Williams"]
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  bookdown::pdf_document2: 
    toc: false
classoption: fleqn
fontfamily: mathpazo
fontsize: 12pt
bibliography: ref_xinhua.bib
link-citations: yes
linkcolor: blue
header-includes:
  - \usepackage{amsmath}
  - \usepackage{setspace}
  - \setlength{\mathindent}{15pt}
  - \setlength\parindent{24pt}
  - \setlength{\parskip}{0.0pt plus 1.0pt}
  - \doublespacing
  - \newtheorem{theorem}{Theorem}[section]
  - \newtheorem{lemma}[theorem]{Lemma}
  - \newtheorem{proposition}[theorem]{Proposition}
  - \newtheorem{corollary}[theorem]{Corollary}
  - \newenvironment{proof}[1][Proof]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries Proof}]}{\end{trivlist}}
  - \newenvironment{definition}[1][Definition]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries 1}]}{\end{trivlist}}
  - \newenvironment{example}[1][Example]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries 1}]}{\end{trivlist}}
  - \newenvironment{remark}[1][Remark]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries 1}]}{\end{trivlist}}
  - \newcommand{\qed}{\nobreak \ifvmode \relax \else
      \ifdim\lastskip<1.5em \hskip-\lastskip
      \hskip1.5em plus0em minus0.5em \fi \nobreak
      \vrule height0.75em width0.5em depth0.25em\fi}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \floatplacement{figure}{!t}
  - \usepackage{caption}\captionsetup[table]{skip=5pt}
  - \usepackage{dcolumn}
  - \usepackage{rotating}
  - \usepackage{indentfirst}
  - \usepackage{caption}\DeclareCaptionLabelFormat{AppendixTables}{A.#2}

abstract: "Absent formal avenues of transparency, how does China publicize its foreign aid and debt allocation efforts? We bring a novel perspective to this issue by considering its international recognition efforts through public diplomacy and news. Chinese. We propose that Beijing’s foreign policy tools, *Xinhua* media coverage of developing countries and bilateral diplomatic activities, are associated with its overseas financing allocation decisions. We expect greater media coverage and bilateral diplomatic activity of a developing country to correlate with more foreign aid giving, but not so much with its debt. It is generally believed that foreign aid is motivated by a country’s developmental needs, hence perceived to be conducive to constructing a positive image of being a donor than lending interest-based debts. To test this expectation, we leverage (1) AidData’s Chinese development finance datasets and (2) the meta-data of millions of *Xinhua* news articles in the Cline Center for Advanced Social Research. We find that China pays more media attention to aid recipients but engages more in diplomatic visits with debtors. Aid-recipient countries disproportionately get more media coverage on the state of their economy and developmental needs. Meanwhile, China is more likely to provide loans to diplomatically aligned countries. Our results dispel the myths that China is a “rouge donor” or a designer of “debt-trap diplomacy.” Instead, we provide suggestive evidence that, much like traditional donors, China’s foreign aid and debt allocations present a versatile foreign policy tool in international politics."
---

@@

Although Beijing has primarily focused on its immediate surrounding neighbors, Asia-Pacific and Central Asia, for security and geostrategic concerns, it is nevertheless increasingly thinking and acting globally [@nathan_chinas_2012]. Similarly, in terms of where China's money goes and its economic influences concentrate, some countries clearly are more important than others. However, Beijing holds the reasons why close to the vest.

The secrecy surrounding China's international development financing is puzzling. But vis-$\grave{\text{a}}$-vis the limited transparency, the painstaking work of researchers to document and analyze trends in China's development financing has illuminated a great deal about Beijing's approach to giving and lending [@dreherEtAl2018; @strange_tracking_2017]. In one of the most comprehensive and thorough efforts to document trends in Chinese development finance, @dreher_banking_2022 find that China is far from the rogue donor that many have feared, but instead, much like these traditional donors, Like traditional Western donors, foreign aid provision is a foreign policy tool to boost the status of the donor country [@ferry_turning_2021]. China's foreign aid can present as a versatile foreign policy tool through which Beijing seeks to accomplish important objectives in international politics. These goals include international recognition that China is a great power and closer diplomatic ties with developing countries in what China calls "South-South" cooperation. In contrast, while arguably China's economic interests seem to play a central role in its allocation of foreign financing activities, empirical evidence does not show associations between Chinese foreign aids and a country's natural resource endowments [@hendrix_confronting_2014; @dreherFuchs2015].

However, the goals of facilitating cooperation and winning international recognition as a rising power are difficult to accomplish in secret. This, therefore, raises a natural question. *Absent formal avenues of transparency, how does China publicize its foreign aid and debt allocation efforts?*

We propose that despite the lack of formal reporting, Beijing's overseas financing allocations go hand in hand with its focus on building allies and shaping foreign public opinions. Specifically, we consider foreign policy tools such as outward-facing state-sponsored news coverage and bilateral diplomatic visits from Beijing. While public diplomacy and outward-facing state-sponsored media are not solely used to support China's overseas development financing, we believe they have clear overlapping purposes. In particular, diplomatic visits and media coverage are critical *visible* activities that can promote the often opaque character of Beijing's development finance. Thus, to the extent that China's development finance is targeted at supporting image- and alliance-building activities, we expect that in general, recipients of China's overseas development assistance will also attract disproportionate attention of media coverage in *Xinhua* to support China's image abroad and to build publicity around its development activities, and they will be more frequent hosts of diplomatic missions from Beijing to support closer bilateral cooperation.

As we test these hypotheses, in our research design we delineate China's development financing according to the type of assistance China offers. Until recently, many have mistakenly conflated Beijing's ODA-like giving with its other official financing (OOF). However, efforts to disentangle China's activities with respect to grants and low-interest loans (financing that would meet the OECD definition of official development assistance or ODA) from its activities with respect to higher interest loans and export credits (OOF) have unmasked a considerable divergence in goals [@dreherEtAl2018]. The conventional view is that while *aid* (ODA) is closely tied to Beijing's foreign policy goals, *debt* (OOF) is related to Beijing's commercial interests.[^1] Thus, as we test our hypotheses, we also distinguish between Beijing-as-donor from Beijing-as-lender. We hypothesize that Beijing intends to be recognized as an altruistic donor but avoids being associated with its intention as a profit-seeking lender. Hence, we develop more fine-grained hypotheses: Aid recipient countries receive more media coverage and diplomatic visits from China, while debt recipient countries do not.

@@

To foreshadow our results, we find that there are very few overlaps between the top 20 countries that receive aid and loans from Beijing at the same time. In other words, China targets its aid and debt to different sets of developing countries. However, the neat distinction between China's use of aid and debt does not imply these tools serve separate goals, policy or commercial oriented ones, as the conventional view holds. In particular, we find that *Xinhua* coverage is disproportionately concentrated among China's aid recipients, while no significant relationship exists between aid and diplomatic visits. Conversely, we find that debt is significantly linked to a greater frequency of bilateral diplomatic missions from Beijing, but no significant difference in *Xinhua* coverage. Together these findings reveal an intriguing pattern: Beijing likes to talk about its aid recipients but prioritizes diplomatic visits with its debtors.

On the one hand, aid recipient countries disproportionately get more media coverage from *Xinhua* via stories that report both on the state of their economy and their development needs. Notably, *Xinhua*'s new stories do not just promote China's efforts to offer aid to those countries in need but also give a rounded picture of those countries' economic conditions justifying their legitimate need for aid. On the other hand, China engages in more conventional forms of bilateral diplomacy via government-to-government diplomatic missions to cement closer bilateral ties with debtors. These findings contradict with what conventional views hold that Beijing has tried to keep its financial assistance secret. Instead, *Xinhua* devotes significant media attention and resources to Beijing's aid recipients. It helps to promote Chinese roles and efforts in the developmental trajectories of these countries and improve Chinese image through visual branding of aid.

Furthermore, in contrast to what conventional wisdom holds, China does not shy away from its ambition in building closer bilateral cooperation with its debt recipients to align with their foreign policy goals. In addition to lending money, China engages in building and strengthening long-term bilateral relationships with these countries. Foreign policy goals play a central role in motivating Beijing's debt allocations. Meanwhile, our finding that Chinese loans corresponding with its diplomatic missions has special relevance in light of Beijing's Belt and Road Initiative (BRI). A 2018 BRI foreign policy assessment report from Washington [@hurley_examining_2019] highlights that lending indicates Beijing's economic interests and strategic dominance  ---  China tends to lend to vulnerable states with debt distress in exchange for unfair deals and strategic concessions. Brautigam [-@brautigam_critical_2020] calls the Chinese "debt-trap diplomacy" as a popularly constructed meme based on collective fear of the Chinese threat rather than sound empirical evidence. Our empirical finding suggests that China is more likely to provide loans to diplomatically aligned countries. For instance, Russia, one of China's closest allies, receives the highest amount of lending on average among 142 countries but no aid at all between 2002 and 2017. In contrast, Iraq shows the opposite pattern: it receives the highest amount of need-based aid from China during the period of our investigation, but it does not receive any loans. Concerns about Chinese debt nonetheless raise a natural question related to the function of diplomacy in debtor countries. Our findings suggest that China's international development program is complex and multifaceted. Does debt serve as a tool of diplomacy, or does Beijing wield diplomacy to cover a multitude of "debt-trap" sins? Our study sheds some new light on this pressing question, but further research is needed to fully answer it.

This paper proceeds as follows. We start by outlining different motivations for China's state financing allocations, followed by discussions of possibly using state-sponsored media and diplomatic visits for Chinese international recognition. We then introduce the variables and model specification strategies in the methods section. Before we show the results from our models, we provide several figures to present our descriptive analysis. Finally, we present our results, with conditional support of our hypotheses, and end with discussions on the implications of our findings.

@@

China's motivations for giving foreign aid to developing countries mirror, in many ways, the motivations of Western donors. While recipient needs, in part, predicate Chinese assistance, so do Beijing's political and economic interests. Evidence suggests that China targets more finance toward poorer countries and does not systematically favor authoritarian over democratic recipients [@dreherEtAl2018]. At the same time, China gives more aid to countries that import more goods from China, while it gives less aid to those that officially recognize Taiwan [@dreherFuchs2015; @dreherEtAl2018]. Further, China's aid disproportionately goes to countries with more natural resources, greater UN General Assembly voting alignment with Beijing, and with more capacity to repay loans [@dreherEtAl2021].

Two waves of surveys of policymakers in 126 countries demonstrate the diplomatic impact that these investments have had.[^2] Compared to a first survey wave in 2014, responses in 2017 showed an increase in evaluations of China's influence with policymakers in developing countries. It would be naive to suppose this is a side-effect, rather than a goal, of China's development finance and other investments. Like the major Western powers, donors of foreign aid is status-conferring: it demonstrates a dedication to helping the needed, improving the audiences' perception of the donor [@goldsmith_doing_2014; @ferry_turning_2021].

@@

If its diplomatic motives for giving aid parallel those of other donor governments, visibility is surely a major concern for Beijing. Visual branding of aid has emerged as a growing concern among donors [@goldsmith_doing_2014]. The United States Agency for International Development (USAID), for example, cited its "new 'brand identity'" as instrumental in promoting the visibility of 2004-2005 tsunami relief to Indonesia.[^3] A US State Department report from 2004 further claims that better branding contributed to a doubling of favorable attitudes toward the US. Pew Research supports this view, finding that nearly 80$\%$ of Indonesians surveyed "said that post-tsunami aid from the US had improved their impression of America."[^4]

@@

On the one hand, since aid is supposed to have more direct links to China's foreign policy goals, it follows that China will complement its aid giving with visible acts of diplomacy and efforts to increase the salience of aid recipients in foreign audiences. On the other hand, while aid and debt may have distinct goals, such a tidy distinction may be too simplistic. Perhaps more importantly, some of the market oriented objectives that drive China's global debt may not benefit from public displays of diplomacy. On this front, recent research suggests that Beijing uses its debt to ensure access to natural resources that China lacks domestically. As noted above, @dreherEtAl2021 find that Beijing targets more of its loans in resource rich developing countries, a strategy that @dreher_banking_2022 contend is meant to guarantee access to said resources. When Beijing's policy banks provide these loans, developing country governments collateralize their oil or rare minerals, all but assuring access to these resources for Beijing since many of these countries are unable to directly repay the loans [@dreher_banking_2022].

@@

This paper will focus on Xinhua outward-facing English branch whose audiences are primarily English-speaking readers. Simply providing more information will not improve their image in the Western world. Attracting audiences depends on credibility, a state-sponsored-image-construction news outlet would typically lack. As Druckman [-@druckman_limits_2001] presents, one conditional factor in influencing public opinion (especially foreign audiences'), is an information sender's "credibility." On the one hand, governments attempt to positively shape the global narrative regarding their leaders and foreign policies using their own newsgathering and broadcasting operations. On the other hand, Xinhua needs to maintain a low political bias and higher professional standard to assert its brand and increase its international competitiveness.

@@

Government-to-government visits are an indicator of the importance the Chinese government places on developing relations with a country as leaders' resources are scarce [@kastner_is_2012]. These visits have both symbolic and functional roles. Diplomatic visits often mark the further development in bilateral relations, especially in furthering the visiting and host countries' bilateral trade relationships [@nitsch_state_2005]. In fact, studies show that diplomatic visits of Chinese leaders lead to stronger commercial ties and surge of investment [@stone_chinese_2022]. For example, Chinese President Xi Jinping promised over 10 billion of investment during a state visit to South Africa. In a news conference hosted by President Cyril Ramaphosa, he demonstrated that “We have agreed that we must work as partners (with China) to improve the lives of our peoples by elevating our business, commercial and trade ties” [@reuter_chinas_2018]. The high-profile leader visits are even used as a proxy for Chinese favor-giving and lobbying for votes in the UN [@wang_leader_2022]. Leader visits also have implications on the host leaders' security in office [@malis_state_2021] and the states' security issues [@mcmanus_making_2018]. In all, diplomatic visits send an important positive signal that the visiting and hosting countries support each other and have close long-term relationships.

Visiting leaders can increase the awareness of themselves and their country among citizens in the host country. Goldsmith and Horiuchi [-@goldsmith_spinning_2009] find that the impact of high-level government visits on foreign publics' opinions is contextual. U.S. visits had large and positive impact until the international media reported the negative aspects of the "war on terror" in Iraq. Again, credibility of a country's leadership is the key to conditioning the effects of high-level visits on the foreign public's perception of the country's policy. The most recent finding shows that high level diplomatic visits across the board can improve the public approval of the visiting leader's job performance by a significantly large effect [@goldsmith_does_2021]. The positive messages are especially contingent on how the public-diplomacy activities are mentioned in the news in the host countries [@goldsmith_does_2021]. In most cases, the host leader has leverage to provide frame for the journalists to report the government-to-government visit that is expected to receive positive coverage.

@@

Since both approaches feature scarce time and resources, we expect that Beijing will choose on whom to cast the spotlight and to visit strategically. Most importantly for China's overseas development financing, media coverage and diplomatic visits are immediate visible signals of Beijing's priorities. For this reason, Beijing may use both as a way to complement related political objectives it seeks to promote via its financing activities.

To test this logic, we examine the extent to which recipients of Chinese overseas development financing also receive disproportionate coverage in *Xinhua* and host a disproportionate number of diplomatic missions from Beijing. We further leverage data both on Chinese ODA (aid) and Chinese OOF (debt) in testing these relationships. As noted earlier, while aid is thought to correspond with Beijing's foreign policy goals, debt is supposedly linked to its commercial goals. The idea is that aid lets Beijing buy influence, whereas debt helps enrich Chinese firms and propel economic growth for China. However, an examination of patterns in the main variables of interest in this study questions this tidy distinction. We therefore expect *Xinhua* coverage and diplomatic visits to be closely linked with Chinese aid, while these outcomes should be independent of Chinese debt.

@@

If we can reject the null hypothesis for H1 and H2, this will be consistent with the view that China's aid givings are compatible with their policy goals. Conversely, H3 and H4 are themselves null hypotheses. If these can be rejected, this will count as evidence that, in fact, debt is neither independent of foreign policy objectives nor tracing commercial interests as the literature claims [@dreher_banking_2022]. The next section describes our data and research design for testing these hypotheses.

@@

To test hypotheses 1-4, we rely on zero-inflated negative binomial regression models using yearly counts at the recipient-year level of the number of *Xinhua* article mentions and the number of bilateral diplomatic visits from Beijing as the response variables, respectively. Since these outcomes reflect discrete counts, we apply a method that explicitly models a discrete count process. We opt for negative binomial regression rather than Poisson since the variance of the outcomes is not equivalent to their means. We further apply the zero-inflated negative binomial model since the distributions of yearly coverage counts and visits contain a substantial number of zero values. Because of the panel nature of the data, we further include random recipient intercepts in model estimation to account for within-recipient dependence and additional unobserved recipient heterogeneity.

@@

Models 1 and 2 each include year intercepts to adjust for yearly shocks and changes to Beijing's overall aid and debt portfolio, denoted by the term $\tau_t$. The parameter $\rho_i$ denotes random recipient intercepts. The vector $X_{it}$ denotes a set of control variables to improve precision and to adjust for possible confounders for Chinese bilateral financing, *Xinhua* coverage, and diplomatic visits. A summary of these variables (four main variables and nine confounders), definitions and their sources is given in the table below.

- Independent variables: `Xinhua's Economic News Articles`, `Diplomatic visits`
- Dependent variables: `Aid`, `Debt`
- Confounders: `UN Vote Agreement (distance)`, `GDP`, `Population`, `Disaster`, `Civil wars`, `Distance`, `Export/Import`, `FDI`, `Democracy Score`

| Variables       | Definitions          | Sources           |
|------------------|------------------------------------------------|--------------|
| `Xinhua's Economic News Articles` | Keywords search[^7] from news headlines to identify relevant news articles and do yearly counts by country. | Global News Archive[^8]|
| `Diplomatic visits`      | Total number of high-level and provincial-level visits by government officials between China and the receiving country each year.| China's Global Public Diplomacy[^9]|
| `Aid`     | Sum of total amounts in dollars of Chinese Official Development Assistance (ODA) to receiving country each year. | Chinese Development Finance[^10]|
| `Debt` | Sum of total amounts in dollars of Chinese Other Official Flows (OOF) to receiving country each year.         | Chinese Development Finance|
| `UN Vote Agreement (distance)` | Aggregated distance of ideal points of UN General Assembly Voting by year        | UN General Assembly Voting Data[^11] |
| `GDP` | PPP GDP of recipient countries is gross domestic product converted to international dollars using purchasing power parity rates (constant 2017 international \$)        | World Bank[^12]|
| `Population` | Total population of recipient countries is based on the de facto definition of population, which counts all residents regardless of legal status or citizenship.        | World Bank|
| `Disaster` | Deaths as a result of natural disasters in recipient countries by year        | Global Burden of Disease Study [^13]|
| `Civil wars` | State-based violent conflicts count of the recipient countries by year        | PRIO Conflict Recurrence Database[^14]|
| `Distance` | Bilateral country distances between recipient countries and China        | CEPII[^15]|
| `Export/Import` | Annual trade statistics between recipient countries and China        | Open Trade Statistics[^16]|
| `FDI` | Foreign direct investment to the recipient countries, net (BoP, current US$) by year       | World Bank|
| `Democracy Score` | Aggregated polyarchy index : To what extent is the electoral principle of democracy achieved?      | V-Dem[^17]|

[^7]: Selecting news articles' headlines that mention one or more of these keywords: aid, donor, lend, development, investment, growth, support, business, help, construction, education, funds, projects, donate, assist
[^8]: @cline_center_for_advanced_social_research_global_2022
[^9]:  @aiddata_aiddata_2021
[^10]: @custer_tracking_2021
[^11]: @voeten_united_2009
[^12]: @world_bank_world_2022
[^13]: @health_metrics_and_evaluation_ihme_global_2019
[^14]: @uppsala_conflict_data_program_ucdp_prio_2020
[^15]: @mayer_notes_2011
[^16]: @vargas_open_2022
[^17]: @coppedge_v-dem_2020

@@

@@
